---
title: "ADM Assignment-1"
author: "Akshaya Mamidipalli"
date: "2024-03-11"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ISLR)
library(dplyr)
```


```{r}
library(glmnet)
```

```{r}
library(caret)
```

```{r}
Carseats_Filtered <- Carseats %>% select("Sales", "Price","Advertising","Population","Age","Income","Education")
```

```{r}
Carseats_Filtered_Normalized <- scale(Carseats_Filtered)
X <- as.matrix(Carseats_Filtered_Normalized[, c('Price','Advertising','Population','Age','Income','Education')])
Y <- Carseats_Filtered_Normalized[,'Sales']
fit.lasso <- glmnet(X,Y,alpha = 1)
plot(fit.lasso,xvar = "lambda")

```


#QB1)

```{r}
lasso_model <- cv.glmnet(X,Y, alpha = 1)
plot(lasso_model)

```
```{r}
best_value <- lasso_model$lambda.min
best_value
```
The best value of the lambda for the lasso- regression model is 0.0015

#QB2)

```{r}
coef(fit.lasso, s=best_value)
```
The coefficient for the price (normalized) attribute in the best model is -4.79 * 10^-1

#QB3)
```{r}
coef(fit.lasso, s=0.01)
```
```{r}
coef(fit.lasso, s=0.1)
```
When the lambda value is set to 0.01, all the attributes remaining in the model with non-zero coefficients.
Nevertheless, the number of attributes with non-zero coefficients drops to four if the lambda value is raised to 0.1. 'Population' and 'Education' attributes are eliminated from the model because their coefficients are practically zero.

#QB4)

```{r}
fit.elastic <- glmnet(X,Y,alpha = 0.6)
plot(fit.elastic,xvar = "lambda")

```

```{r}
elastic_model <- cv.glmnet(X,Y, alpha = 0.6)
plot(elastic_model)

```
```{r}
best_value_elastic <- elastic_model$lambda.min
best_value_elastic

```
The best value of the lambda for an elastic-net model is 0.0023

